---
title: "w4_assignment"
author: ""
date: "21/9/2021"
output: html_document
---

Here, i am using the pacman package to load/install tidyverse and the here package.  

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(tidyverse, here)
```

Creating the vector called rooms. 
Then i am calling plyr from the tidyverse to count the elements in the rooms vector.
The count is then piped to the filter function to only get the elements that are equal to or above 3.
This result is saved as a dataframe.
Finally i am printing the sum of the freq column to get the total number of elements. 

```{r}
rooms <- c(1, 2, 1, 3, 1, NA, 3, 1, 3, 2, 1, NA, 1, 8, 3, 1, 4, NA, 1, 3, 1, 2, 1, 7, 1, NA)

df <- plyr::count(rooms) %>% 
  filter(x >= 3)

print(sum(df$freq))
```

Here, i am using the base function typeof() to get the type of the rooms vector.
It outputs that the type is a 'double' meaning that it is an integer value with no comma values (float).

```{r}
typeof(rooms)
```

Here i am using the median function on the rooms vector. 
Initially, the output is NA because the vector includes NA's. This is always the result if it includes NA, because statistics cannot be computed on missing values. 
In the seconf line of code i am specifying that NA's should be removed. Therefore the result is now 1.5. 

```{r}
median(rooms)
median(rooms, na.rm = T)
```

Here i am using the download.file() function to get the safi file.

```{r}
download.file("https://ndownloader.figshare.com/files/11492171",
              "data/SAFI_clean.csv", mode = "wb")
```

Now i am using the read_csv() function to load the csv file as the name 'interviews'.

```{r}
interviews <- read_csv('data/SAFI_clean.csv', na = 'NULL')
```

